FTLR proof cases

### 2018-06-26 fully-abstract-comp/ftlr-proof-cases.tex
merge

\begin{lemma}[Capability splicing retains safety for normal capabilities]
  \label{lem:splitting-safety-normal}
  If
  \begin{itemize}
  \item $\npair{(c_1,c_1)} \in \lrvg{\trust}(W_1)$
  \item $\npair{(c_2,c_2)} \in \lrvg{\trust}(W_2)$
  \item $c_1 = ((\perm,\lin),\baddr,n,\aaddr)$
  \item $c_2 = ((\perm,\lin),n,\eaddr,\aaddr)$
  \item $c = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
  \item $b \le n \le e$
  \item $c_1' = \linCons{c_1}$
  \item $c_2' = \linCons{c_2}$
  \end{itemize}
  then there exist $W_1',W_2',W_3'$ such that
  \begin{itemize}
  \item $W_1 \oplus W_2 = W_1' \oplus W_2' \oplus W_3'$
  \item $\npair{(c,c)} \in \lrvg{\trust}(W_3')$
  \item $\npair{(c_1',c_1')} \in \lrvg{\trust}(W_1')$
  \item $\npair{(c_2',c_2')} \in \lrvg{\trust}(W_2')$
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}

\begin{lemma}[Capability splicing retains safety for stack capabilities]
  \label{lem:splitting-safety-stack}
  If
  \begin{itemize}
  \item $\npair{(c_{1,S},c_{1,T})} \in \lrvg{\trust}(W_1)$
  \item $\npair{(c_{2,S},c_{2,T})} \in \lrvg{\trust}(W_2)$
  \item $b \le n \le e$
  \item $c_{1,S} = \stkptr{\perm,\baddr,n,\aaddr}$
  \item $c_{1,T} = ((\perm,\linear),\baddr,n,\aaddr)$
  \item $c_{2,S} = \stkptr{\perm,n,\eaddr,\aaddr}$
  \item $c_{2,T} = ((\perm,\linear),n,\eaddr,\aaddr)$
  \item $c_S = \stkptr{\perm,\baddr,\eaddr,\aaddr}$
  \item $c_T = ((\perm,\linear),\baddr,\eaddr,\aaddr)$
  \item $c_{1,S}' = c_{1,T}' = 0$
  \item $c_{2,S}' = c_{2,T}' = 0$
  \end{itemize}
  then there exist $W_1',W_2',W_3'$ such that
  \begin{itemize}
  \item $W_1 \oplus W_2 = W_1' \oplus W_2' \oplus W_3'$
  \item $\npair{(c_S,c_T)} \in \lrvg{\trust}(W_3')$
  \item $\npair{(c_{1,S}',c_{1,T}')} \in \lrvg{\trust}(W_1')$
  \item $\npair{(c_{2,S}',c_{2,T}')} \in \lrvg{\trust}(W_2')$
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}

@@

  \item \label{case:ftlr:move-cca-etc} All of the following hold: (includes cap-manipulation cases: move, cca,
    restrict, seta2b, cseal, split, splice, that can be handled mostly
    uniformly)
    \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r_1\cdots r_k}{w_1\cdots w_k}}\neq
      \failed$
    \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r_1\cdots r_k}{w_1'\cdots w_k'}}
      \neq \failed$
    \item One of the following holds:
      \item \label{case:ftlr:move-cca-etc:cca-normal} (restrict,cca,seta2b) $w_1 = ((\perm',\lin),\baddr,\eaddr,\aaddr')$,
        $w_1' = ((\perm',\lin),\baddr,\eaddr,\aaddr')$, $\Phi_S(r_1) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\Phi_T(r_1) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\perm' \sqsubseteq\perm$, $k =
        1$
      \item \label{case:ftlr:move-cca-etc:cca-stack}(restrict,cca,seta2b) $w_1 = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$,
        $w_1' = ((\perm',\linear),\baddr,\eaddr,\aaddr')$, $\Phi_S(r_1) =
        \stkptr{\perm,\baddr,\eaddr,\aaddr}$ and $\Phi_T(r_1) =
        ((\perm,\linear),\baddr,\eaddr,\aaddr)$ and $\perm' \sqsubseteq\perm$,
        $k = 1$
      \item \label{case:ftlr:move-cca-etc:cca-seal}(cca,seta2b) $w_1 = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$,
        $w_1' = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$, $\Phi_S(r_1) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$ and $\Phi_T(r_1) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $k = 1$
      \item \label{case:ftlr:move-cca-etc:move}(move) $w_1 = \Phi_S(r_2)$, $w_1' = \Phi_T(r_2)$, and $\isLinear{w_1} \Rightarrow w_2 = w_2' = 0$, and $\neg \isLinear{w_1} \Rightarrow (w_2 = \Phi_S(r_2) \wedge w_2' = \Phi_T(r_2)$) and $r_1 \neq r_2$ and $k = 2$.
      \item \label{case:ftlr:move-cca-etc:move-eq}(move) $w_1 = \Phi_S(r_1)$, $w_1' = \Phi_T(r_1)$ and $k = 1$.
      \item \label{case:ftlr:move-cca-etc:cseal}(cseal) $w_1 = \sealed{\sigma,\Phi_S(r_1)}$, $w_1' =
        \sealed{\sigma,\Phi_T(r_1)}$, $\Phi_S(r_2) = \Phi_T(r_2) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $k=1$
      \item \label{case:ftlr:move-cca-etc:split-normal} (split) $\Phi_T(r_3) = \Phi_S(r_3) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\baddr \leq n$, $n < \eaddr$,
        $w_1 = w_1' = ((\perm,\lin),\baddr,n,\aaddr)$, $w_2 = w_2' =
        ((\perm,\lin),n+1,\eaddr,\aaddr)$, $w_3 = w_3' = \linCons{\Phi_S(r_3)}$, $k=3$.
      \item \label{case:ftlr:move-cca-etc:split-seal} (split) $\Phi_T(r_3) = \Phi_S(r_3) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $\sigma_\baddr \leq n$, $n <
        \sigma_\eaddr$, $w_1 = w_1' = \seal{\sigma_\baddr,n,\sigma}$, $w_2 =
        w_2' = \seal{n+1,\sigma_\eaddr,\sigma}$, $k=2$.
      \item \label{case:ftlr:move-cca-etc:split-stack} (split) $\Phi_S(r_3) = \stkptr{\perm,\baddr,\eaddr,\aaddr}$,
        $\Phi_T(r_3) = ((\perm,\linear),\baddr,\eaddr,\aaddr)$, $\baddr \leq n$,
        $n < \eaddr$, $w_1 = \stkptr{\perm,\baddr,n,\aaddr}$, $w_1' =
        ((\perm,\linear),\baddr,n,\aaddr)$, $w_2 =
        \stkptr{\perm,n+1,\eaddr,\aaddr}$, $w_2' =
        ((\perm,\linear),n+1,\eaddr,\aaddr)$, $w_3 = w_3' = 0$, $k=3$.
      \item \label{case:ftlr:move-cca-etc:splice-stack}(splice) $\Phi_T(r_2) = ((\perm,\linear),\baddr_2,\eaddr_2,\_)$,
        $\Phi_S(r_2) = \stkptr{\perm,\baddr_2,\eaddr_2,\_}$, and $\Phi_T(r_3) =

@@

        ((\perm,\lin),\eaddr_2+1,\eaddr_3,\aaddr_3)$, and $\baddr_2 \leq

@@

  By assumption we have
  \[
    \npair[n]{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)
  \]
  which gives us $R_R : (\RegName \setminus \{\pcreg\}) \fun World$ such that $W_R = \bigoplus_{r\in \RegName \setminus \{\pcreg\}} R_R(r)$ and for all $r$ in $\RegName \setminus \{\pcreg\}$ we have $\npair[n]{(\Phi_S.\reg(r),\Phi_T.\reg(r))} \in \lrrg{\trust}(R_R(r))$.
  To this end, we need to consider each of cases \ref{case:ftlr:move-cca-etc:cca-normal}-\ref{case:ftlr:move-cca-etc:splice-seal}:
  \begin{itemize}
  \item Case \ref{case:ftlr:move-cca-etc:cca-normal}:

@@

  \item Case \ref{case:ftlr:move-cca-etc:move}:

@@

    By the above points, by assumption and using Lemma~\ref{lem:downwards-closed}, we then have for all $r$ that:
    \[
      \npair[n-1]{(\Phi_S'(r), \Phi_T'(r))} \in \lrvg{\trust}(R_R'(r))
    \]
  \item Case \ref{case:ftlr:move-cca-etc:split-seal}:
    In this case, we can take $R_R' = R_R$ and use Lemma~\ref{lem:purePart-oplus} to give us that all $\purePart{R_R(r)}$ are equal.
    For $r = r_1, r_2, r_3$, we then get easily by definition that
    \[
      \npair[n-1]{(\Phi_S'(r), \Phi_T'(r))} \in \lrvg{\trust}(R_R'(r))
    \]
    and for other registers, it follows by Lemma~\ref{lem:downwards-closed}.

  \item Case \ref{case:ftlr:move-cca-etc:split-stack}:

@@

TODO
  \item Case \label{case:ftlr:move-cca-etc:splice-seal}:

>>>>

\begin{lemma}[Capability splicing retains safety for normal capabilities]
  \label{lem:splitting-safety-normal}
  If
  \begin{itemize}
  \item $\npair{(c_1,c_1)} \in \lrvg{\trust}(W_1)$
  \item $\npair{(c_2,c_2)} \in \lrvg{\trust}(W_2)$
  \item $c_1 = ((\perm,\lin),\baddr,n,\aaddr)$
  \item $c_2 = ((\perm,\lin),n,\eaddr,\aaddr)$
  \item $c = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
  \item $b \le n \le e$
  \item $c_1' = \linCons{c_1}$
  \item $c_2' = \linCons{c_2}$
  \end{itemize}
  then there exist $W_1',W_2',W_3'$ such that
  \begin{itemize}
  \item $W_1 \oplus W_2 = W_1' \oplus W_2' \oplus W_3'$
  \item $\npair{(c,c)} \in \lrvg{\trust}(W_3')$
  \item $\npair{(c_1',c_1')} \in \lrvg{\trust}(W_1')$
  \item $\npair{(c_2',c_2')} \in \lrvg{\trust}(W_2')$
  \end{itemize}
\end{lemma}
\begin{proof}
TODO

Copy paste from work on ftlr proof case:

    First we only consider registers $r_1,r_2,r_3$.

    If $\isLinear{(\Phi_S(r_3))}$, then we need to redistribute the ownership
    previously owned by the world used for $r_3$ to $r_1$ and $r_2$.

    From $\npair{(\Phi_S(r_3),\Phi_S(r_3))} \in \lrvg{\trust}(R_R(r_3))$, we get that either $\perm = \noperm$, in which case we can pick the ownership distribution to be the same as before, or $\npair{[\baddr,\eaddr]} \in \readCond{\linear,R_R(r_3)}$.

    In the latter case, we get $S \subseteq \addressable{\linear,\pwheap{R_R(r_3)}}$ and $R : S \fun \powerset{R_R(r_3)}$ such that $\forall r \in S \ldotp |R(r)| = 1$ and $\biguplus_{r\in S} R(r) \supseteq [\baddr,\eaddr]$.

    Now we have to argue the following:
    \begin{itemize}
    \item if $\perm \in \readAllowed$, then
      \begin{itemize}
      \item $\npair{[\baddr,s]} \in \readCond{\linear,R_R'(r_1)}$
      \item $\npair{[s+1,\eaddr]} \in \readCond{R_R'(r_2)}$
      \end{itemize}
      Both follow from the assumption $\npair{[\baddr,\eaddr]} \in \readCond{\linear,R_R(r_3)}$, and the fact that $R_R'(r_i), i=1,2$ owns the appropriate regions.
    \item if $\perm \in \writeAllowed$, then
      \begin{itemize}
      \item $\npair{[\baddr,s]} \in \writeCond{\linear,R_R'(r_1)}$
      \item $\npair{[s+1,\eaddr]} \in \writeCond{\linear,R_R'(r_2)}$
      \end{itemize}
      Both follow from the assumption $\npair{[\baddr,\eaddr]} \in \writeCond{\linear,R_R(r_3)}$, and the fact that $R_R'(r_i), i=1,2$ owns the appropriate regions.
    \item $\perm = \rwx$

      By assumption.
    \item $\perm \neq \rx$

      Assuming $\perm = \rx$, then it must have been the case that $\lin = \normal$ contradicting the assumption $\isLinear{(\Phi_S(r_3))}$.
    \end{itemize}

    We also trivially have $\npair[n-1]{(0,0)} \in \lrv{R_R'(r_3)}$ which shows the content of register $r_3$ to be safe.

    If $\neg \isLinear{(\Phi_S(r_3))}$, then we pick $R_R' = R_R$.
    In this case, we need to show
    \begin{itemize}
    \item if $\perm \in \readAllowed$, then
      \begin{itemize}
      \item $\npair[n-1]{[\baddr,s]} \in \readCond{\normal,R_R'(r_1)}$
      \item $\npair[n-1]{[s+1,\eaddr]} \in \readCond{R_R'(r_2)}$
      \end{itemize}
      This follows by assumption, Lemma~\ref{lem:conds-shrinkable}, Lemma~\ref{lem:non-linear-pure}, and Lemma~\ref{lem:monotonicity}.
    \item if $\perm \in \writeAllowed$, then
      \begin{itemize}
      \item $\npair[n-1]{[\baddr,s]} \in \writeCond{\normal,R_R'(r_1)}$
      \item $\npair[n-1]{[s+1,\eaddr]} \in \writeCond{\normal,R_R'(r_2)}$
      \end{itemize}
      This follows by assumption, Lemma~\ref{lem:conds-shrinkable}, Lemma~\ref{lem:non-linear-pure}, and Lemma~\ref{lem:monotonicity}.
    \item $\perm \neq \rwx$

      By assumption.
    \item if $\perm = \rx$, then 
      \begin{itemize}
      \item $\npair[n-1]{[\baddr,s]} \in \xReadCond{R_R'(r_1)}$
      \item $\npair[n-1]{[s+1,\eaddr]} \in \xReadCond{R_R'(r_2)}$
      \item $\npair[n-1]{[\baddr,s]} \in \execCond{R_R'(r_1)}$
      \item $\npair[n-1]{[s+1,\eaddr]} \in \execCond{R_R'(r_2)}$
      \end{itemize}
      All of the above follow by assumption, Lemma~\ref{lem:conds-shrinkable}, Lemma~\ref{lem:non-linear-pure}, and Lemma~\ref{lem:monotonicity}.
    \end{itemize}

    Finally, we have
    \[
      \npair[n-1]{\Phi_S'(r_3),\Phi_T'(r_3)}\in \lrv{R_R'(3)}
    \]
    by assumption and Lemma~\ref{lem:downwards-closed}.

\begin{lemma}[Capability splicing retains safety for stack capabilities]
  \label{lem:splitting-safety-stack}
  If
  \begin{itemize}
  \item $\npair{(c_{1,S},c_{1,T})} \in \lrvg{\trust}(W_1)$
  \item $\npair{(c_{2,S},c_{2,T})} \in \lrvg{\trust}(W_2)$
  \item $b \le n \le e$
  \item $c_{1,S} = \stkptr{\perm,\baddr,n,\aaddr}$
  \item $c_{1,T} = ((\perm,\linear),\baddr,n,\aaddr)$
  \item $c_{2,S} = \stkptr{\perm,n,\eaddr,\aaddr}$
  \item $c_{2,T} = ((\perm,\linear),n,\eaddr,\aaddr)$
  \item $c_S = \stkptr{\perm,\baddr,\eaddr,\aaddr}$
  \item $c_T = ((\perm,\linear),\baddr,\eaddr,\aaddr)$
  \item $c_{1,S}' = c_{1,T}' = 0$
  \item $c_{2,S}' = c_{2,T}' = 0$
  \end{itemize}
  then there exist $W_1',W_2',W_3'$ such that
  \begin{itemize}
  \item $W_1 \oplus W_2 = W_1' \oplus W_2' \oplus W_3'$
  \item $\npair{(c_S,c_T)} \in \lrvg{\trust}(W_3')$
  \item $\npair{(c_{1,S}',c_{1,T}')} \in \lrvg{\trust}(W_1')$
  \item $\npair{(c_{2,S}',c_{2,T}')} \in \lrvg{\trust}(W_2')$
  \end{itemize}
\end{lemma}
\begin{proof}
TODO

  copy paste from FTLR proof

      We need to redistribute the ownership previously owned by the world used for $r_3$ to $r_1$ and $r_2$.

    From $\npair{(\Phi_S(r_3),\Phi_S(r_3))} \in \lrvg{\trust}(R_R(r_3))$, we get that either $\perm = \noperm$, in which case we can pick the ownership distribution to be the same as before, or $\npair{[\baddr,\eaddr]} \in \stackReadCond{R_R(r_3)}$.

    In the latter case, we get $S \subseteq \addressable{\linear,\pwfree{R_R(r_3)}}$ and $R : S \fun \powerset{R_R(r_3)}$ such that $\forall r \in S \ldotp |R(r)| = 1$ and $\biguplus_{r\in S} R(r) \supseteq [\baddr,\eaddr]$.

    Now we have to argue the following:
    \begin{itemize}
    \item if $\perm \in \readAllowed$, then
      \begin{itemize}
      \item $\npair{[\baddr,s]} \in \stackReadCond{\linear,R_R'(r_1)}$
      \item $\npair{[s+1,\eaddr]} \in \stackReadCond{R_R'(r_2)}$
      \end{itemize}
      Both follow from the assumption $\npair{[\baddr,\eaddr]} \in \stackReadCond{\linear,R_R(r_3)}$, and the fact that $R_R'(r_i), i=1,2$ owns the appropriate regions.
    \item if $\perm \in \writeAllowed$, then
      \begin{itemize}
      \item $\npair{[\baddr,s]} \in \stackWriteCond{\linear,R_R'(r_1)}$
      \item $\npair{[s+1,\eaddr]} \in \stackWriteCond{\linear,R_R'(r_2)}$
      \end{itemize}
      Both follow from the assumption $\npair{[\baddr,\eaddr]} \in \stackWriteCond{\linear,R_R(r_3)}$, and the fact that $R_R'(r_i), i=1,2$ owns the appropriate regions.
    \end{itemize}

    We also trivially have $\npair[n-1]{(0,0)} \in \lrv{R_R'(r_3)}$ which shows the content of register $r_3$ to be safe.

    For regions $r \neq r_1,r_2,r_3$, we have
    \[
      \npair[n-1]{(\Phi_S'(r), \Phi_T'(r))} \in \lrvg{\trust}(R(r))
    \]
    by assumption and Lemma~\ref{lem:downwards-closed}.

@@

    \end{itemize}
  \item \label{case:ftlr:move-cca-etc} All of the following hold: (includes cap-manipulation cases: move, cca,
    restrict, seta2b, cseal, split, splice, that can be handled mostly
    uniformly)
    \begin{itemize}
    \item $\Phi_S \step[\gc] \Phi_S'$
    \item $\Phi_T \step \Phi_T'$
    \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r_1\cdots r_k}{w_1\cdots w_k}}\neq
      \failed$
    \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r_1\cdots r_k}{w_1'\cdots w_k'}}
      \neq \failed$
    \item One of the following holds:
      \begin{enumproof}
      \item \label{case:ftlr:move-cca-etc:cca-normal} (restrict,cca,seta2b) $w_1 = ((\perm',\lin),\baddr,\eaddr,\aaddr')$,
        $w_1' = ((\perm',\lin),\baddr,\eaddr,\aaddr')$, $\Phi_S(r_1) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\Phi_T(r_1) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\perm' \sqsubseteq\perm$, $k =
        1$
      \item \label{case:ftlr:move-cca-etc:cca-stack}(restrict,cca,seta2b) $w_1 = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$,
        $w_1' = ((\perm',\linear),\baddr,\eaddr,\aaddr')$, $\Phi_S(r_1) =
        \stkptr{\perm,\baddr,\eaddr,\aaddr}$ and $\Phi_T(r_1) =
        ((\perm,\linear),\baddr,\eaddr,\aaddr)$ and $\perm' \sqsubseteq\perm$,
        $k = 1$
      \item \label{case:ftlr:move-cca-etc:cca-seal}(cca,seta2b) $w_1 = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$,
        $w_1' = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$, $\Phi_S(r_1) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$ and $\Phi_T(r_1) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $k = 1$
      \item \label{case:ftlr:move-cca-etc:move}(move) $w_1 = \Phi_S(r_2)$, $w_1' = \Phi_T(r_2)$, and $\isLinear{w_1} \Rightarrow w_2 = w_2' = 0$, and $\neg \isLinear{w_1} \Rightarrow (w_2 = \Phi_S(r_2) \wedge w_2' = \Phi_T(r_2)$) and $r_1 \neq r_2$ and $k = 2$.
      \item \label{case:ftlr:move-cca-etc:move-eq}(move) $w_1 = \Phi_S(r_1)$, $w_1' = \Phi_T(r_1)$ and $k = 1$.
      \item \label{case:ftlr:move-cca-etc:cseal}(cseal) $w_1 = \sealed{\sigma,\Phi_S(r_1)}$, $w_1' =
        \sealed{\sigma,\Phi_T(r_1)}$, $\Phi_S(r_2) = \Phi_T(r_2) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $k=1$
      \item \label{case:ftlr:move-cca-etc:split-normal} (split) $\Phi_T(r_3) = \Phi_S(r_3) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\baddr \leq s$, $s < \eaddr$,
        $w_1 = w_1' = ((\perm,\lin),\baddr,n,\aaddr)$, $w_2 = w_2' =
        ((\perm,\lin),n+1,\eaddr,\aaddr)$, $w_3 = w_3' = \linCons{\Phi_S(r_3)}$, $k=3$.
      \item \label{case:ftlr:move-cca-etc:split-seal} (split) $\Phi_T(r_3) = \Phi_S(r_3) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $\sigma_\baddr \leq s$, $s <
        \sigma_\eaddr$, $w_1 = w_1' = \seal{\sigma_\baddr,s,\sigma}$, $w_2 =
        w_2' = \seal{s+1,\sigma_\eaddr,\sigma}$, $k=2$.
      \item \label{case:ftlr:move-cca-etc:split-stack} (split) $\Phi_S(r_3) = \stkptr{\perm,\baddr,\eaddr,\aaddr}$,
        $\Phi_T(r_3) = ((\perm,\linear),\baddr,\eaddr,\aaddr)$, $\baddr \leq s$,
        $s < \eaddr$, $w_1 = \stkptr{\perm,\baddr,n,\aaddr}$, $w_1' =
        ((\perm,\linear),\baddr,s,\aaddr)$, $w_2 =
        \stkptr{\perm,s+1,\eaddr,\aaddr}$,

        $w_2' = ((\perm,\linear),s+1,\eaddr,\aaddr)$, $k=2$.
      \item \label{case:ftlr:move-cca-etc:splice-stack}(splice) $\Phi_T(r_2) = ((\perm,\linear),\baddr_2,\eaddr_2,\_)$,
        $\Phi_S(r_2) = \stkptr{\perm,\baddr_2,\eaddr_2,\_}$, and

        $\Phi_T(r_3) =

@@

        ((\perm,\lin),\eaddr_2+1,\eaddr_3,\aaddr_3)$, and
        $\baddr_2 \leq

@@

  By assumption we have
  \[
    \npair[n]{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)
  \]
  which gives us $R_R : (\RegName \setminus \{\pcreg\}) \fun World$ such that $W_R = \bigoplus_{r\in \RegName \setminus \{\pcreg\}} R_R(r)$ and for all $r$ in $\RegName \setminus \{\pcreg\}$ we have $\npair[n]{(\Phi_S.\reg(r),\Phi_T.\reg(r))} \in \lrrg{\trust}(R_R(r))$.
  To this end, we need to consider each of cases
  \ref{case:ftlr:move-cca-etc:cca-normal}-\ref{case:ftlr:move-cca-etc:splice-seal}:

  TODO: check that all the below cases take care of the trusted case.
  \begin{itemize}
  \item Case \ref{case:ftlr:move-cca-etc:cca-normal}:

@@

  \item Case \ref{case:ftlr:move-cca-etc:move}:
    TODO: check if this case considers the trusted case.

@@

    By the above points, by assumption and using Lemma~\ref{lem:downwards-closed}, we then have for all $r$ that:
    \[
      \npair[n-1]{(\Phi_S'(r), \Phi_T'(r))} \in \lrvg{\trust}(R_R'(r))
    \]
  \item Case \ref{case:ftlr:move-cca-etc:split-seal}:
    In this case, we can take $R_R' = R_R$ and use Lemma~\ref{lem:purePart-oplus} to give us that all $\purePart{R_R(r)}$ are equal.
    For $r = r_1, r_2, r_3$, we then get easily by definition that
    \[
      \npair[n-1]{(\Phi_S'(r), \Phi_T'(r))} \in \lrvg{\trust}(R_R'(r))
    \]
    and for other registers, it follows by Lemma~\ref{lem:downwards-closed}.
  \item Case \ref{case:ftlr:move-cca-etc:split-stack}:
    First we only consider registers $r_1,r_2,r_3$.

@@

    We start by arguing the safety of $r_1$:

    If the permission is $\noperm$, then it is trivial to show.

    Assuming the permission is not $\noperm$, we know $\perm \in \readAllowed{}$.

    If we further assume $\isLinear{\Phi_S(r_2)}$
    \begin{itemize}
    \item $\npair{[\baddr_2,\eaddr_2]} \in \readCond{\linear,R_R(r_2)}$
    \item $\npair{[\eaddr_2+1,\eaddr_3]} \in \readCond{\linear,R_R(r_3)}$
    \end{itemize}
    From this we get $S_2 \subseteq \addressable{\linear,\pwheap{R_R(r_2)}}$ and
    $R_2 : S_2 \fun \powerset{\nats}$ such that $\forall r \in S_2 \ldotp
    |R_2(r)| = 1$ (and so on) as well as $S_3 \subseteq \addressable{\linear,\pwheap{R_R(r_3)}}$ and
    $R_3 : S_3 \fun \powerset{\nats}$ such that $\forall r \in S_3 \ldotp
    |R_3(r)| = 1$ (and so on).

    In $R_R'$ give $r_1$ ownership of $R_2^{-1}([\baddr_2,\eaddr_2])$ and $R_3^{-1}([\baddr_2+1,\eaddr_3])$ and removed it from the respective regions that owned it before.
    The remaining ownership remains unchanged.

    Now we need to show
    \[
      \npair[n-1]{[\baddr_2,\eaddr_3]} \in \readCond{\linear,R_R(r_2)}
    \]
    which we do by picking $S' = S_2 \cup S_3$ and $R'(r) = R_2(r)$ for $r \in S_2$ and $R'(r) = R_3(r)$ for $r \in S_3$.
    With these choices, the rest follow by the readCondition assumptions and downwards-closure.

    If $\perm \in \writeAllowed{}$, then we need to show
    \[
      \npair[n-1]{[\baddr_2,\eaddr_3]} \in \writeCond{\linear,R_R(r_2)}
    \]
    which is done in a similar fashion\footnote{We do technically need to argue that the readCondition and the writeCondition agree on the set of regions we got from the readCondition.
      This is done using the memory satisfaction assumption.}.

    Using the same ownership distribution, it is trivial to show
    \[
      \npair[n-1]{(\Phi_S'(r_i),\Phi_T'(r_i))} \in \lrv(R'_R(r_i)) \text{ for $i
        \in \{1,2\}$}
    \]
    as the pair is $(0,0)$.

    For $\neg \isLinear{\Phi_S(r_2)}$, we use $R_R' = R_R$ as the distribution function.
    In this case, for $r_1$ it works like before, i.e.\ the result follows from the assumptions.
    However, in the case where the permission is $\rx$, we also have to show the following:
    \begin{itemize}
    \item $\npair[n-1]{[\baddr_2,\eaddr_3]} \in \xReadCond{R_R'(r_1)}$

      By assumption we have
      \begin{itemize}
      \item $\npair{[\baddr_2,\eaddr_2]} \in \xReadCond{\linear,R_R(r_2)}$
      \item $\npair{[\eaddr_2+1,\eaddr_3]} \in \xReadCond{\linear,R_R(r_3)}$
      \end{itemize}
      From which the result follows.
    \item $\npair[n-1]{[\baddr_2,\eaddr_3]} \in \execCond{R_R'(r_1)}$

      TODO
    \end{itemize}

    For regions $r \neq r_1,r_2,r_3$, we have
    \[
      \npair[n-1]{(\Phi_S'(r), \Phi_T'(r))} \in \lrvg{\trust}(R(r))
    \]
    by assumption and Lemma~\ref{lem:downwards-closed}.

  \item Case \label{case:ftlr:move-cca-etc:splice-seal}:
